---
title: "SDVC Final Report Descriptive Tables"
subtitle: "Dairy Practices : Knowledge and Practice of Cow Rearing"
author: "Julia Silge"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: yes
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
library(ggplot2)
theme_set(theme_light())
```

Before we make some pretty tables, let's read in the data.

```{r}
library(readr)
library(forcats)
library(dplyr)
library(reshape2)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))
dim(gpf_ppt)

gpf_ppt <- gpf_ppt %>%
    filter(round %in% c('1.0', '5.0')) %>%
    mutate(round_month = fct_recode(round,
                              `Jul 2014` = '1.0',
                              `Jul 2016` = '5.0')) %>%
    mutate(household_type = fct_collapse(household_type,
                                         Treatment = c("1", "2", "3"),
                                         Control = c("4", "5", "6")))

gpf_ppt[,c(1,27:35,36,273:276,326)] <- lapply(gpf_ppt[,c(1,27:35,36,273:276,326)], as.numeric)
```

## Make a Producers Data Frame

```{r}
producers <- bind_rows(gpf_ppt %>% 
                           filter(round_month == 'Jul 2014') %>% 
                           distinct(entry_id, .keep_all = TRUE),
                       gpf_ppt %>%
                           filter(round_month == 'Jul 2016') %>%
                           distinct(household_type, deo_id, round, .keep_all = TRUE))
                    
dim(producers)    
```

## 1. Fodder – who is involved, types cultivated

```{r, fig.width=8, fig.height=4}
library(tidyr)
producers <- producers %>%
    mutate(are_you_cultivating_fodder = fct_recode(are_you_cultivating_fodder,
                              `Yes` = '1',
                              `No` = '2',
                              `Do not know how to cultivate` = '3',
                              `Have no land/scope` = '0')) %>%
    mutate(are_you_cultivating_fodder = fct_relevel(are_you_cultivating_fodder, 
                                                    "Yes", "No", "Do not know how to cultivate"))

totals <- producers %>% 
    group_by(round_month, household_type, are_you_cultivating_fodder) %>% 
    summarise(n = n()) %>% 
    filter(!is.na(are_you_cultivating_fodder) & are_you_cultivating_fodder != '9') %>%
    group_by(round_month, household_type) %>% 
    summarise(total = sum(n, na.rm = TRUE))


df <- producers %>% 
    group_by(round_month, household_type, are_you_cultivating_fodder) %>% 
    summarise(n = n()) %>%
    filter(!is.na(are_you_cultivating_fodder) & are_you_cultivating_fodder != '9') %>%
    left_join(totals, by = c("round_month", "household_type")) %>%
    mutate(prop = n / total*100) %>%
    select(-n, -total) %>%
    complete(are_you_cultivating_fodder) %>%
    filter(are_you_cultivating_fodder != "9")
 
df %>%
    kable(digits = 1,
          col.names = c("Round of Data Collection", "Treatment/Control",
                        "Are You Cultivating Fodder?", "Percent"),
          caption = "Treatment and Control Groups at the First and Last Data Collection Rounds")

ggplot(df, aes(round_month, prop/100, fill = are_you_cultivating_fodder)) +
    geom_bar(alpha = 0.8, stat = "identity", position = "dodge") +
    facet_wrap(~household_type) +
    labs(x = NULL, y = "Are You Cultivating Fodder?") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme(legend.title=element_blank())

```

```{r, fig.width=8, fig.height=4}
producers$type_fodder_cultivating[producers$type_fodder_cultivating == 0] <- NA
producers <- producers %>%
    mutate(type_fodder_cultivating = fct_recode(type_fodder_cultivating,
                              Napier = '1',
                              Sorghum = '2',
                              Maize = '3',
                              German = '5',
                              Jamboo = '6',
                              `Kheshari/MatiKalai` = '7',
                              Other = '9')) %>%
    mutate(type_fodder_cultivating = fct_collapse(type_fodder_cultivating,
                                                  Multiple = c("1,2",
                                                               "1,3",
                                                               "1,3,4",
                                                               "1,3,7",
                                                               "1,5",
                                                               "1,5,6",
                                                               "1,6",
                                                               "1,6,7",
                                                               "1,7",
                                                               "1.7",
                                                               "14",
                                                               "1m6",
                                                               "1,99",
                                                               "2,3",
                                                               "2,7",
                                                               "3,1",
                                                               "3,6",
                                                               "6,7",
                                                               "6,1"))) %>%
    mutate(type_fodder_cultivating = fct_relevel(type_fodder_cultivating,
                                                 "German",
                                                 "Jamboo", 
                                                 "Kheshari/MatiKalai", 
                                                 "Maize", 
                                                 "Napier",
                                                 "Sorghum",
                                                 "Other",
                                                 "Multiple"))

totals <- producers %>% 
    group_by(round_month, household_type, type_fodder_cultivating) %>% 
    summarise(n = n()) %>% 
    filter(!is.na(type_fodder_cultivating)) %>%
    group_by(round_month, household_type) %>% 
    summarise(total = sum(n, na.rm = TRUE))


df <- producers %>% 
    group_by(round_month, household_type, type_fodder_cultivating) %>% 
    summarise(n = n()) %>%
    filter(!is.na(type_fodder_cultivating)) %>%
    left_join(totals, by = c("round_month", "household_type")) %>%
    mutate(prop = n / total*100) %>%
    select(-n, -total) %>%
    complete(type_fodder_cultivating)
 
df %>%
    kable(digits = 1,
          col.names = c("Round of Data Collection", "Treatment/Control",
                        "What Type of Fodder Are You Cultivating?", "Percent"),
          caption = "Treatment and Control Groups at the First and Last Data Collection Rounds")

ggplot(df, aes(round_month, prop/100, fill = type_fodder_cultivating)) +
    geom_bar(alpha = 0.8, stat = "identity", position = "dodge") +
    facet_wrap(~household_type) +
    labs(x = NULL, y = "What Type of Fodder Are You Cultivating?") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme(legend.title=element_blank())

```

## 2. Green Grass

```{r, fig.height=4, fig.width=8}
producers <- producers %>%
    mutate(do_you_feed_green_grass_to_cow = fct_recode(do_you_feed_green_grass_to_cow,
                              `Yes` = '1',
                              `No` = '2'))

totals <- producers %>% 
    group_by(round_month, household_type, do_you_feed_green_grass_to_cow) %>% 
    summarise(n = n()) %>% 
    filter(!is.na(do_you_feed_green_grass_to_cow)) %>%
    group_by(round_month, household_type) %>% 
    summarise(total = sum(n, na.rm = TRUE))


df <- producers %>% 
    group_by(round_month, household_type, do_you_feed_green_grass_to_cow) %>% 
    summarise(n = n()) %>%
    filter(!is.na(do_you_feed_green_grass_to_cow)) %>%
    left_join(totals, by = c("round_month", "household_type")) %>%
    mutate(prop = n / total*100) %>%
    select(-n, -total)
 
df %>%
    kable(digits = 1,
          col.names = c("Round of Data Collection", "Treatment/Control",
                        "Do You Feed Green Grass to Your Cattle?", "Percent"),
          caption = "Treatment and Control Groups at the First and Last Data Collection Rounds")

ggplot(df, aes(round_month, prop/100, fill = do_you_feed_green_grass_to_cow)) +
    geom_bar(alpha = 0.8, stat = "identity", position = "dodge") +
    facet_wrap(~household_type) +
    labs(x = NULL, y = "Do You Feed Green Grass to Your Cattle?") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme(legend.title=element_blank())

```

```{r, fig.height=4, fig.width=8}
producers$source_grass[producers$source_grass == 0] <- NA
producers$source_grass[producers$source_grass == '5'] <- NA

producers <- producers %>%
    mutate(source_grass = fct_recode(source_grass,
                              `Own production` = '1',
                              Purchase = '2',
                              `Collected road side/field` = '3',
                              Grazing = '4')) %>%
    mutate(source_grass = fct_collapse(source_grass,
                                       Multiple = c("1,2",
                                                    "1,2,3",
                                                    "1,2,4",
                                                    "1,3",
                                                    "1,4",
                                                    "1,6",
                                                    "1,9",
                                                    "1.,2",
                                                    "1.2",
                                                    "1.3",
                                                    "1.4",
                                                    "14,2",
                                                    "1m2",
                                                    "1m3",
                                                    "2,1",
                                                    "2,3",
                                                    "2,4",
                                                    "2,8",
                                                    "3,2",
                                                    "3,4",
                                                    "3,8",
                                                    "3.4",
                                                    "4,3"))) %>%
    mutate(source_grass = fct_relevel(source_grass,
                                      "Own production",
                                      "Purchase",
                                      "Collected road side/field",
                                      "Grazing",
                                      "Multiple"))

totals <- producers %>% 
    group_by(round_month, household_type, source_grass) %>% 
    summarise(n = n()) %>% 
    filter(!is.na(source_grass)) %>%
    group_by(round_month, household_type) %>% 
    summarise(total = sum(n, na.rm = TRUE))


df <- producers %>% 
    group_by(round_month, household_type, source_grass) %>% 
    summarise(n = n()) %>%
    filter(!is.na(source_grass)) %>%
    left_join(totals, by = c("round_month", "household_type")) %>%
    mutate(prop = n / total*100) %>%
    select(-n, -total) %>%
    complete(source_grass)
 
df %>%
    kable(digits = 1,
          col.names = c("Round of Data Collection", "Treatment/Control",
                        "Source of Grass", "Percent"),
          caption = "Treatment and Control Groups at the First and Last Data Collection Rounds")

ggplot(df, aes(round_month, prop/100, fill = source_grass)) +
    geom_bar(alpha = 0.8, stat = "identity", position = "dodge") +
    facet_wrap(~household_type) +
    labs(x = NULL, y = "Source of Grass") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme(legend.title=element_blank())

```

## 3. Deworming

```{r, fig.height=4, fig.width=8}
producers$have_you_dewormed_cattle_in_last_6_months[producers$have_you_dewormed_cattle_in_last_6_months == 0] <- NA
producers <- producers %>%
    mutate(have_you_dewormed_cattle_in_last_6_months = fct_recode(have_you_dewormed_cattle_in_last_6_months,
                                                                  `Yes` = '1',
                                                                  `No` = '2'))

totals <- producers %>% 
    group_by(round_month, household_type, have_you_dewormed_cattle_in_last_6_months) %>% 
    summarise(n = n()) %>% 
    filter(!is.na(have_you_dewormed_cattle_in_last_6_months)) %>%
    group_by(round_month, household_type) %>% 
    summarise(total = sum(n, na.rm = TRUE))


df <- producers %>% 
    group_by(round_month, household_type, have_you_dewormed_cattle_in_last_6_months) %>% 
    summarise(n = n()) %>%
    filter(!is.na(have_you_dewormed_cattle_in_last_6_months)) %>%
    left_join(totals, by = c("round_month", "household_type")) %>%
    mutate(prop = n / total*100) %>%
    select(-n, -total)
 
df %>%
    kable(digits = 1,
          col.names = c("Round of Data Collection", "Treatment/Control",
                        "Have You Dewormed Your Cattle (Last 6 Months)?", "Percent"),
          caption = "Treatment and Control Groups at the First and Last Data Collection Rounds")

ggplot(df, aes(round_month, prop/100, fill = have_you_dewormed_cattle_in_last_6_months)) +
    geom_bar(alpha = 0.8, stat = "identity", position = "dodge") +
    facet_wrap(~household_type) +
    labs(x = NULL, y = "Have You Dewormed Your Cattle (Last 6 Months)?") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme(legend.title=element_blank())

```


## 4. Washing

## 5. Bio-Security

## 6. Vaccination

## 7. Artificial Insemination (usage, costs, and source)

## 8. Diet of the herd (breakdown of what the cows eat and farmer expenditure on cattle diet)

## 9. Relationship between expenditure on cow diet and cow production levels

## 10. Cow purchase history – proportion of farmers, median count by breed value

## 11. Cow selling history – proportion of farmers, median count by breed value

## 12. Calf history

## 13. Knowledge Scores

## 14. Practice Score

## 15. Source of financing of dairy activities

## 16. Size of loans

