---
title: "SDVC Final Report Descriptive Tables"
subtitle: "Dairy Cattle Inventory and Milk Production"
author: "Julia Silge"
date: "`r Sys.Date()`"
output: word_document
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

Before we make some pretty tables, let's read in the data.

```{r}
library(readr)
library(forcats)
library(dplyr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))
dim(gpf_ppt)

gpf_ppt <- gpf_ppt %>%
    mutate(round = as.numeric(round)) %>%
    mutate(sex_respondent = fct_recode(sex_respondent,
                                       Female = "1", Male = "2", Others = "3"))
```

## Herd Demographics

```{r}


    
```


## Cattle inventory by household, by district

```{r}
gpf_ppt <- gpf_ppt %>%
    mutate(number_cattle_breed_1 = as.numeric(number_cattle_breed_1),
           number_cattle_breed_2 = as.numeric(number_cattle_breed_2))

kable(
    gpf_ppt %>% 
        filter(!is.na(round)) %>%
        group_by(household_type, sex_respondent, round, district_gpf) %>%
        summarise(avgcows = mean(number_cattle_breed_1 + number_cattle_breed_2, na.rm = TRUE),
                  mediancows = median(number_cattle_breed_1 + number_cattle_breed_2, na.rm = TRUE)) %>%
        filter(!is.na(mediancows)),
    digits = 2,
    col.names = c("Treatment/Control Group", "Gender", "Round of Data Collection", 
                  "District", "Number of Cows per Household (Average)", "Number of Cows per Household (Median)")
)

```


## Number of local breed cattle per household, per district

## Number of cross breed cattle per household, per district

## Percentage of in-milking cows

## Number of births per cow, per district

## Value of local breed and cross breed cows in BDT, by district

## Value of Herd

## Productivity of Herd

## Daily household production of cows in liters, by district, by breed

## Total Income from Milk Sales (Tk.) per month

## Total Milk Consumption in Liters

## Milk Consumption Priorities

## Milk Distribution Patterns – litres

## Milk Distribution Patterns – percentages

## Market Linkage Choices
