---
title: "First Attempts at Modeling"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

It is now time to do some modeling. Here is our general plan:

For the treatment groups, we will 

* build a linear model
* build a linear mixed effects model using `group_code` as the random effect

For the treatment + control groups, we will

* only use linear models


## Loading the Data

First, let's load the data , do some cleaning that we found we needed to do during the table-making process, and make a producers data frame. The producers data frame needs to include the number of in-milk cows (both breeds) and the quantity of milk produced yesterday.

```{r setup}
library(readr)
library(dplyr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))

gpf_ppt$district_gpf[gpf_ppt$district_gpf == "pabna"] <- "Pabna"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Jaipur Hat"] <- "Joypurhat"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Natore"] <- "Nator"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgong"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgonj"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajgang"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajganj"] <- "Sirajgonj"

gpf_ppt[,c(28:35)] <- lapply(gpf_ppt[,c(28:35)], as.numeric)

## code below makes producer data frame with in-milk local breed cows, 
## in-milk cross breed cows, total number of all cows, and total liters 
## produced yesterday

producers <- bind_rows(gpf_ppt %>% 
                           filter(round == '1.0') %>% 
                           distinct(entry_id, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         group_by(entry_id) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_cross_cows = n())),
                       gpf_ppt %>%
                           filter(round != '1.0') %>%
                           distinct(household_type, deo_id, round, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_cross_cows = n()))) %>%
    rowwise() %>%
    mutate(total_distribution_yesterday = sum(total_free_distribution_ltr,
                                              neighbors,
                                              collection_point,
                                              milk_collector,
                                              open_market,
                                              sweetmeat_tea_stall,
                                              direct_to_company,
                                              yesterday_total_spoilage_ltr,
                                              na.rm = TRUE)) %>%
    ungroup

producers <- producers %>%
    mutate(yesterday_total_income_from_milk_sale = as.numeric(yesterday_total_income_from_milk_sale),
           round = as.factor(round),
           district_gpf = as.factor(district_gpf),
           group_code = as.factor(group_code),
           household_type = as.factor(household_type))

producers$yesterday_total_income_from_milk_sale[producers$yesterday_total_income_from_milk_sale == 0.0] <- NA
producers$total_distribution_yesterday[producers$total_distribution_yesterday == 0.0] <- NA
producers$in_milk_cross_cows[is.na(producers$in_milk_cross_cows)] <- 0
producers$in_milk_local_cows[is.na(producers$in_milk_local_cows)] <- 0

dim(producers)    
```

## Make Two Data Frames

We will build different models for the treatment and treatment + control producers, so let's be explicit about that right here.

```{r}
all_producers <- producers

treatment_producers <- producers %>%
    filter(household_type %in% c("1", "2", "3"))
```

## Building a Model for the Treatment Groups

```{r}
library(lme4)

## fix up the group codes at all?

treatment_producers %>% 
    group_by(round) %>% 
    summarise(n = n(), 
              group_code_NA = mean(is.na(group_code)))

fit_me <- lmer(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday +
                 (1 | group_code),
             data = treatment_producers)


fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = treatment_producers)


summary(fit_me)
summary(fit_lm)
```

## Building a Model for the Treatment and Control Groups

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = all_producers)
summary(fit_lm)
```


## Current Issues

* The mixed effects model still says it is rank deficient.
* The linear models have singularities so some coefficients are not defined.

These sound like they are the same problem, right? Like there is not enough information in our data to constrain the model we are trying to build? What would be a good next step?

Including the total liters distributed obviously has a super big effect, and the R squared is already quite high. Let's just look at those two variables.

```{r, fig.width=8, fig.height=6}
library(ggplot2)
ggplot(all_producers, aes(total_distribution_yesterday, 
                          yesterday_total_income_from_milk_sale, 
                          color = round)) +
    geom_point(size = 2, alpha = 0.5) +
    facet_wrap(~household_type) +
    theme_light() +
    labs(title = "Income vs. Liters of Milk Distributed",
         subtitle = "Each panel shows a different treatment/control group")
```


One idea I have here is to make one treatment group and one control group and trying modeling with that; there's just not much data in some of these bins.
