---
title: "First Attempts at Modeling"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

It is now time to do some modeling. Here is our general plan:

For the treatment groups, we will 

* build a linear model
* build a linear mixed effects model using `group_code` as the random effect

For the treatment + control groups, we will

* only use linear models


## Loading the Data

First, let's load the data , do some cleaning that we found we needed to do during the table-making process, and make a producers data frame. The producers data frame needs to include the number of in-milk cows (both breeds) and the quantity of milk produced yesterday.

```{r setup}
library(readr)
library(dplyr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))

gpf_ppt$district_gpf[gpf_ppt$district_gpf == "pabna"] <- "Pabna"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Jaipur Hat"] <- "Joypurhat"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Natore"] <- "Nator"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgong"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgonj"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajgang"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajganj"] <- "Sirajgonj"

gpf_ppt[,c(28:35)] <- lapply(gpf_ppt[,c(28:35)], as.numeric)

## code below makes producer data frame with in-milk local breed cows, 
## in-milk cross breed cows, total number of all cows, and total liters 
## produced yesterday

producers <- bind_rows(gpf_ppt %>% 
                           filter(round == '1.0') %>% 
                           distinct(entry_id, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         group_by(entry_id) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_cross_cows = n())),
                       gpf_ppt %>%
                           filter(round != '1.0') %>%
                           distinct(household_type, deo_id, round, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_cross_cows = n()))) %>%
    rowwise() %>%
    mutate(total_distribution_yesterday = sum(total_free_distribution_ltr,
                                              neighbors,
                                              collection_point,
                                              milk_collector,
                                              open_market,
                                              sweetmeat_tea_stall,
                                              direct_to_company,
                                              yesterday_total_spoilage_ltr,
                                              na.rm = TRUE)) %>%
    ungroup

producers <- producers %>%
    mutate(yesterday_total_income_from_milk_sale = as.numeric(yesterday_total_income_from_milk_sale),
           round = as.factor(round),
           district_gpf = as.factor(district_gpf),
           group_code = as.factor(group_code),
           household_type = as.factor(household_type))

producers$yesterday_total_income_from_milk_sale[producers$yesterday_total_income_from_milk_sale == 0.0] <- NA
producers$total_distribution_yesterday[producers$total_distribution_yesterday == 0.0] <- NA
producers$in_milk_cross_cows[is.na(producers$in_milk_cross_cows)] <- 0
producers$in_milk_local_cows[is.na(producers$in_milk_local_cows)] <- 0

dim(producers)    
```

## Make Two Data Frames

We will build different models for the treatment and treatment + control producers, so let's be explicit about that right here.

```{r}
all_producers <- producers

treatment_producers <- producers %>%
    filter(household_type %in% c("1", "2", "3"))
```

## Building a Model for the Treatment Groups

These first models don't work so well because there is not enough information in our data to constrain this model.

```{r}
library(lme4)

## fix up the group codes at all?

treatment_producers %>% 
    group_by(round) %>% 
    summarise(n = n(), 
              group_code_NA = mean(is.na(group_code)))

fit_me <- lmer(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday +
                 (1 | group_code),
             data = treatment_producers)


fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = treatment_producers)


summary(fit_me)
summary(fit_lm)
```

RANK DEFICIENT. AND SINGULARITIES.

What if we try a model with only treatment groups 1 and 2?

```{r}
treatment_producers_subset <- treatment_producers %>%
    filter(household_type == 1 | household_type == 2)

fit_me <- lmer(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday +
                 (1 | group_code),
             data = treatment_producers_subset)


fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = treatment_producers_subset)


summary(fit_me)
summary(fit_lm)
```

This is functioning better, at least the `lm` version.

## Building a Model for the Treatment and Control Groups

Again, we can't build a good, functioning model with all treatment/control groups and rounds because not all groups were surveyed in all rounds.

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = all_producers)
summary(fit_lm)
```

What about all groups in rounds 1 and 5?

```{r}
all_producers_rounds <- all_producers %>%
    filter(round == '1.0' | round == '5.0')

fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = all_producers_rounds)
summary(fit_lm)

```

Still some singularities.

What about collapsing all the separate treatment and control groups into just one group each?

```{r}
library(forcats)
all_producers_collapse <- all_producers %>%    
    mutate(household_type = fct_collapse(household_type,
                                         Treatment = c("1", "2", "3"),
                                         Control = c("4", "5", "6"))) %>%
    filter(round == '1.0' | round == '5.0')

fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = all_producers_collapse)
summary(fit_lm)

```


That looks much better. Neither the regular slope or interaction term with the household type are significant in this model. 

There are significant district-to-district differences, and the number of in-milk cows and total liters distributed significantly affect income. Cross breed cows more strongly impact income than local breed cows.

## Plotting the Data

A lot of these models still have issues, but let's plot the data. The total liters distributed is the most important effect, and the R squared is quite high for all of the models. Let's plot those two variables.

```{r, fig.width=8, fig.height=6}
library(ggplot2)
ggplot(all_producers, aes(total_distribution_yesterday, 
                          yesterday_total_income_from_milk_sale, 
                          color = round)) +
    geom_point(size = 2, alpha = 0.5) +
    facet_wrap(~household_type) +
    theme_light() +
    labs(title = "Income vs. Liters of Milk Distributed",
         subtitle = "Each panel shows a different treatment/control group")
```
