---
title: "First Attempts at Modeling"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

It is now time to do some modeling. Here is our general plan:

For the treatment groups, we will 

* build a linear model
* build a linear mixed effects model using `group_code` as the random effect

For the treatment + control groups, we will

* only use linear models


## Loading the Data

First, let's load the data , do some cleaning that we found we needed to do during the table-making process, and make a producers data frame. The producers data frame needs to include the number of in-milk cows (both breeds) and the quantity of milk produced yesterday.

```{r setup}
library(readr)
library(dplyr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))

gpf_ppt$district_gpf[gpf_ppt$district_gpf == "pabna"] <- "Pabna"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Jaipur Hat"] <- "Joypurhat"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Natore"] <- "Nator"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgong"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgonj"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajgang"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajganj"] <- "Sirajgonj"

gpf_ppt[,c(28:35)] <- lapply(gpf_ppt[,c(28:35)], as.numeric)

## code below makes producer data frame with in-milk local breed cows, 
## in-milk cross breed cows, total number of all cows, and total liters 
## produced yesterday

producers <- bind_rows(gpf_ppt %>% 
                           filter(round == '1.0') %>% 
                           distinct(entry_id, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         group_by(entry_id) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_cross_cows = n())),
                       gpf_ppt %>%
                           filter(round != '1.0') %>%
                           distinct(household_type, deo_id, round, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_cross_cows = n()))) %>%
    rowwise() %>%
    mutate(total_distribution_yesterday = sum(total_free_distribution_ltr,
                                              neighbors,
                                              collection_point,
                                              milk_collector,
                                              open_market,
                                              sweetmeat_tea_stall,
                                              direct_to_company,
                                              yesterday_total_spoilage_ltr,
                                              na.rm = TRUE)) %>%
    ungroup

producers <- producers %>%
    mutate(yesterday_total_income_from_milk_sale = as.numeric(yesterday_total_income_from_milk_sale),
           round = as.factor(round),
           district_gpf = as.factor(district_gpf),
           group_code = as.factor(group_code),
           household_type = as.factor(household_type))

producers$yesterday_total_income_from_milk_sale[producers$yesterday_total_income_from_milk_sale == 0.0] <- NA
producers$total_distribution_yesterday[producers$total_distribution_yesterday == 0.0] <- NA

dim(producers)    
```

## Make Two Data Frames

We will build different models for the treatment and treatment + control producers, so let's be explicit about that right here.

```{r}
all_producers <- producers

treatment_producers <- producers %>%
    filter(household_type %in% c("1", "2", "3"))
```

## Building a Model for the Treatment Groups

```{r}
library(lme4)

## fix up the group codes at all?

treatment_producers %>% 
    group_by(round) %>% 
    summarise(n = n(), 
              group_code_NA = mean(is.na(group_code)))

fit_me <- lmer(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday +
                 (1 | group_code),
             data = treatment_producers)


fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = treatment_producers)


summary(fit_me)
summary(fit_lm)
```

## Building a Model for the Treatment and Control Groups

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows +
                 total_distribution_yesterday,
             data = all_producers)
summary(fit_lm)
```

## Counting `NA` Values

The modeling is not working so well right now, I think because so many rows are getting thrown out because of missing data. How many observations do we have if we want to use all of these columns?

```{r}
mean(complete.cases(all_producers %>% 
                        select(yesterday_total_income_from_milk_sale, 
                               round, 
                               household_type, 
                               district_gpf, 
                               in_milk_cross_cows, 
                               in_milk_local_cows, 
                               total_distribution_yesterday)))

sum(complete.cases(all_producers %>% 
                       select(yesterday_total_income_from_milk_sale, 
                              round, 
                              household_type, 
                              district_gpf, 
                              in_milk_cross_cows, 
                              in_milk_local_cows, 
                              total_distribution_yesterday)))
```

So there are only 110 producers in the treatment + control groups (less than 2% of the data) that have non-`NA` values for all of these columns.

What about just the treatment producers?

```{r}
mean(complete.cases(treatment_producers %>% 
                        select(yesterday_total_income_from_milk_sale, 
                               round, 
                               household_type, 
                               district_gpf, 
                               in_milk_cross_cows, 
                               in_milk_local_cows, 
                               total_distribution_yesterday)))

sum(complete.cases(treatment_producers %>% 
                       select(yesterday_total_income_from_milk_sale, 
                              round, 
                              household_type, 
                              district_gpf, 
                              in_milk_cross_cows, 
                              in_milk_local_cows, 
                              total_distribution_yesterday)))
```

Here it is only 78 producers (about the same, less than 2%) that have non-`NA` values for all of these columns.

Which of these columns are really killing us for missing data?

```{r}
all_producers %>% 
    summarise(`NA income` = mean(is.na(yesterday_total_income_from_milk_sale)),
              `NA round` = mean(is.na(round)),
              `NA hhtype` = mean(is.na(household_type)),
              `NA district` = mean(is.na(district_gpf)),
              `NA crossbreed` = mean(is.na(in_milk_cross_cows)),
              `NA local` = mean(is.na(in_milk_local_cows)),
              `NA liters` = mean(is.na(total_distribution_yesterday)))
```

So it is the income, number of in-milk cows of both breeds, and liters of milk distributed that are really killing us here. The `NA` values are so high that I am not sure imputation methods such as random forest would be at all effective. One idea would be to put zeroes in for all the `NA` values for number of in-milk cows. That would at least give us ~40%  of the data in income and liters distributed.

```{r}
mean(complete.cases(all_producers %>% 
                        select(yesterday_total_income_from_milk_sale, 
                               total_distribution_yesterday)))

sum(complete.cases(all_producers %>% 
                       select(yesterday_total_income_from_milk_sale, 
                              total_distribution_yesterday)))
```

Fortunately, most of the non-missing data for those two columns are the same rows. What do you think of that plan? Is an `NA` for the number of in-milk cows mostly the same as a zero for in-milk cows?
