---
title: "First Attempts at Modeling"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

It is now time to do some modeling. Here we go!

## Loading the Data

First, let's load the data , do some cleaning that we found we needed to do during the table-making process, and make a producers data frame. The producers data frame needs to include the number of in-milk cows (both breeds) and the quantity of milk produced yesterday.

```{r}
library(readr)
library(dplyr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))

gpf_ppt$district_gpf[gpf_ppt$district_gpf == "pabna"] <- "Pabna"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Jaipur Hat"] <- "Joypurhat"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Natore"] <- "Nator"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgong"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgonj"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajgang"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajganj"] <- "Sirajgonj"

producers <- bind_rows(gpf_ppt %>% 
                           filter(round == '1.0') %>% 
                           distinct(entry_id, .keep_all = TRUE),
                       gpf_ppt %>%
                           filter(round != '1.0') %>%
                           distinct(household_type, deo_id, round, .keep_all = TRUE))
## add in-milk local breed cows, in-milk cross breed cows, total number of 
## cows, and total liters produced yesterday

producers[,c(36)] <- lapply(producers[,c(36)], as.numeric)

producers[,c(1,13,24,281)] <- lapply(producers[,c(1,13,24,281)], as.factor)

dim(producers)    

# make treatment only producers data frame
```

## Building a Model

Random effects will have different intercepts

Fixed effect vs. random effect

```{r}
library(lme4)
library(broom)

## fix up the group codes -- ALL A MESS
## producer ID = group code + 2 digits at end

fit1 <- lmer(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf +
                 (1 | group_code),
             data = producers)

summary(fit1)
```

For treatment group,

* Do linear model
* Do lme model using group_code

For treatment + control group

* Only use linear models
