---
title: "Predicting Total Milk Produced"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

Let's build a model to predict total milk produced (in liters) for the treatment and control groups at rounds 1 and 5.

## Loading and Processing the Data

First, let's load the data, do some cleaning that we found we needed to do during the table-making process, and make a producers data frame. The producers data frame needs to include the number of in-milk cows (both breeds) and the quantity of milk produced yesterday.

```{r setup}
library(readr)
library(dplyr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))

gpf_ppt$district_gpf[gpf_ppt$district_gpf == "pabna"] <- "Pabna"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Jaipur Hat"] <- "Joypurhat"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Natore"] <- "Nator"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgong"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgonj"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajgang"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajganj"] <- "Sirajgonj"

gpf_ppt[,c(27:35)] <- lapply(gpf_ppt[,c(28:35)], as.numeric)

## code below makes producer data frame with in-milk local breed cows, 
## in-milk cross breed cows, total number of all cows, and total liters 
## produced yesterday

producers <- bind_rows(gpf_ppt %>% 
                           filter(round == '1.0') %>% 
                           distinct(entry_id, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         group_by(entry_id) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_cross_cows = n())),
                       gpf_ppt %>%
                           filter(round != '1.0') %>%
                           distinct(household_type, deo_id, round, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_cross_cows = n()))) %>%
    rowwise() %>%
    mutate(total_distribution_yesterday = sum(total_consumption_ltr,
                                              total_free_distribution_ltr,
                                              neighbors,
                                              collection_point,
                                              milk_collector,
                                              open_market,
                                              sweetmeat_tea_stall,
                                              direct_to_company,
                                              yesterday_total_spoilage_ltr,
                                              na.rm = TRUE)) %>%
    ungroup

producers <- producers %>%
    mutate(yesterday_total_income_from_milk_sale = as.numeric(yesterday_total_income_from_milk_sale),
           round = as.factor(round),
           district_gpf = as.factor(district_gpf),
           group_code = as.factor(group_code),
           household_type = as.factor(household_type))

producers$yesterday_total_income_from_milk_sale[producers$yesterday_total_income_from_milk_sale == 0.0] <- NA
producers$total_distribution_yesterday[producers$total_distribution_yesterday == 0.0] <- NA
producers$in_milk_cross_cows[is.na(producers$in_milk_cross_cows)] <- 0
producers$in_milk_local_cows[is.na(producers$in_milk_local_cows)] <- 0

dim(producers)    
```


## Building a Model with Number of Cows

Let's collapse all the separate treatment and control groups into just one group each.

```{r}
library(forcats)
all_producers_collapse <- producers %>%    
    mutate(household_type = fct_collapse(household_type,
                                         Treatment = c("1", "2", "3"),
                                         Control = c("4", "5", "6"))) %>%
    filter(round == '1.0' | round == '5.0')

fit_lm <- lm(total_distribution_yesterday ~ round * household_type +
                 in_milk_cross_cows + in_milk_local_cows,
             data = all_producers_collapse)
summary(fit_lm)

```


Let's try a similar model without the interaction term.

```{r}
fit_lm <- lm(total_distribution_yesterday ~ round + household_type +
                 in_milk_cross_cows + in_milk_local_cows,
             data = all_producers_collapse)
summary(fit_lm)
```

Pretty much the same. Still no significant effect between the treatment/control group.

## Building a Model with Three-Way Interaction Including Gender

```{r}
fit_respondent <- lm(total_distribution_yesterday ~ in_milk_cross_cows + in_milk_local_cows +
                 round * household_type * sex_respondent,
             data = all_producers_collapse)
summary(fit_respondent)
```


```{r}
fit_rearing <- lm(total_distribution_yesterday ~ in_milk_cross_cows + in_milk_local_cows +
                 round * household_type * cow_rearing,
             data = all_producers_collapse)
summary(fit_rearing)
```


## Visualization of Models

Let's make some visualization of these last couple of models.

```{r}
pred <- expand.grid(in_milk_cross_cows = c(0,1,2,3,4),
                    in_milk_local_cows = 0,
                    round = c('1.0', '5.0'),
                    household_type = levels(all_producers_collapse$household_type),
                    sex_respondent = c('1','2'),
                    cow_rearing = c('1','2','3'))

pred$pred1 <- predict(fit_respondent, newdata = pred)
pred$pred2 <- predict(fit_rearing, newdata = pred)
```


```{r, fig.width=8, fig.height=6}
library(ggplot2)
ggplot(pred, aes(in_milk_cross_cows, pred1, color = sex_respondent)) +
    geom_line(size = 1.5, alpha = 0.8) +
    facet_grid(round ~ household_type) +
    labs(y = "Total liters of milk distributed",
         x = "Number of in-milk cross breed cows")
```

Respondent sex of 1 means female and 2 means male. I could make this plot with the local breed cows instead if you'd like.

```{r, fig.width=8, fig.height=6}
ggplot(pred, aes(in_milk_cross_cows, pred2, color = cow_rearing)) +
    geom_line(size = 1.5, alpha = 0.8) +
    facet_grid(round ~ household_type) +
    labs(y = "Total liters of milk distributed",
         x = "Number of in-milk cross breed cows")


```

Cow rearing coded as 1 means female, 2 means male, and 3 means jointly.
