---
title: "Predicting Income from Milk Sales"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

Let's build a model to predict income from milk sales for the treatment and control groups at rounds 1 and 5.

## Loading and Processing the Data

First, let's load the data, do some cleaning that we found we needed to do during the table-making process, and make a producers data frame. The producers data frame needs to include the number of in-milk cows (both breeds) and the quantity of milk produced yesterday.

```{r setup}
library(readr)
library(dplyr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))

gpf_ppt$district_gpf[gpf_ppt$district_gpf == "pabna"] <- "Pabna"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Jaipur Hat"] <- "Joypurhat"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Natore"] <- "Nator"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgong"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Shirajgonj"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajgang"] <- "Sirajgonj"
gpf_ppt$district_gpf[gpf_ppt$district_gpf == "Sirajganj"] <- "Sirajgonj"

gpf_ppt[,c(28:35)] <- lapply(gpf_ppt[,c(28:35)], as.numeric)

## code below makes producer data frame with in-milk local breed cows, 
## in-milk cross breed cows, total number of all cows, and total liters 
## produced yesterday

producers <- bind_rows(gpf_ppt %>% 
                           filter(round == '1.0') %>% 
                           distinct(entry_id, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         group_by(entry_id) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round == '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(entry_id) %>% 
                                         summarize(in_milk_cross_cows = n())),
                       gpf_ppt %>%
                           filter(round != '1.0') %>%
                           distinct(household_type, deo_id, round, .keep_all = TRUE) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(total_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 1) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_local_cows = n())) %>%
                           left_join(gpf_ppt %>% 
                                         filter(round != '1.0') %>% 
                                         filter(cow_type == 1, cow_breed == 2) %>% 
                                         group_by(household_type, deo_id, round) %>% 
                                         summarize(in_milk_cross_cows = n()))) %>%
    rowwise() %>%
    mutate(total_distribution_yesterday = sum(total_free_distribution_ltr,
                                              neighbors,
                                              collection_point,
                                              milk_collector,
                                              open_market,
                                              sweetmeat_tea_stall,
                                              direct_to_company,
                                              yesterday_total_spoilage_ltr,
                                              na.rm = TRUE)) %>%
    ungroup

producers <- producers %>%
    mutate(yesterday_total_income_from_milk_sale = as.numeric(yesterday_total_income_from_milk_sale),
           round = as.factor(round),
           district_gpf = as.factor(district_gpf),
           group_code = as.factor(group_code),
           household_type = as.factor(household_type))

producers$yesterday_total_income_from_milk_sale[producers$yesterday_total_income_from_milk_sale == 0.0] <- NA
producers$total_distribution_yesterday[producers$total_distribution_yesterday == 0.0] <- NA
producers$in_milk_cross_cows[is.na(producers$in_milk_cross_cows)] <- 0
producers$in_milk_local_cows[is.na(producers$in_milk_local_cows)] <- 0

dim(producers)    
```


## Building a Model with Number of Cows

Let's collapse all the separate treatment and control groups into just one group each.

```{r}
library(forcats)
all_producers_collapse <- producers %>%    
    mutate(household_type = fct_collapse(household_type,
                                         Treatment = c("1", "2", "3"),
                                         Control = c("4", "5", "6"))) %>%
    filter(round == '1.0' | round == '5.0')

fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows,
             data = all_producers_collapse)
summary(fit_lm)

```


Neither the regular slope or interaction term with the household type are significant in this model. There are some significant district-to-district differences, and the number of in-milk cows and total liters distributed significantly affect income. Cross breed cows more strongly impact income than local breed cows. Income is higher at round 5 than round 1.

Let's try a similar model without the interaction term.

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round + household_type +
                 district_gpf + in_milk_cross_cows + in_milk_local_cows,
             data = all_producers_collapse)

summary(fit_lm)
```

Pretty much the same. Still no significant effect between the treatment/control group.

## Building a Model with Total Liters of Milk Distributed

Now let's try models with the total liters distributed instead of number of cows.

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 district_gpf + total_distribution_yesterday,
             data = all_producers_collapse)

summary(fit_lm)
```

Very similar. Neither the regular slope nor interaction term with treatment/control is significant. There are more district-to-district differences that are significant than for the number of cows, and income is higher a) at round 5 and b) for more liters of milk distributed.

What if we take out the interaction term?

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round + household_type +
                 district_gpf + total_distribution_yesterday,
             data = all_producers_collapse)

summary(fit_lm)
```

Pretty much the same.

## Models with Gender

Does the gender of the person who answers the survey (this is the owner, right?) or the person engaged in cow rearing effect income?

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round + household_type +
                 district_gpf + total_distribution_yesterday +
                 sex_respondent + cow_rearing,
             data = all_producers_collapse)

summary(fit_lm)
```

Nothing much here.

Is there an interaction between treatment/control and gender?

```{r}
fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round + household_type +
                 district_gpf + total_distribution_yesterday +
                 sex_respondent * household_type,
             data = all_producers_collapse)

summary(fit_lm)
```

Probably not.

## Models without District

Let's try a few models without district as a predictor. What about ones with number of cows?

```{r}

fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 in_milk_cross_cows + in_milk_local_cows,
             data = all_producers_collapse)
summary(fit_lm)

fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round + household_type +
                 in_milk_cross_cows + in_milk_local_cows,
             data = all_producers_collapse)
summary(fit_lm)

```

What about ones with liters of milk distributed?

```{r}

fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round * household_type +
                 total_distribution_yesterday,
             data = all_producers_collapse)
summary(fit_lm)

fit_lm <- lm(yesterday_total_income_from_milk_sale ~ round + household_type +
                 total_distribution_yesterday,
             data = all_producers_collapse)
summary(fit_lm)

```
