---
title: "Merging the PPT and GPF Datasets"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

It is now time to merge the PPT and GFP datasets. Let's do it!

## Reading in Both Sets of Data

```{r}
library(readr)
gpf <- read_csv("../data/gpf_merged.csv", 
                col_types = cols(.default = col_character()))
dim(gpf)
ppt <- read_csv("../data/ppt_merged.csv", 
                col_types = cols(.default = col_character()))
dim(ppt)
```

First, let's get the PPT data ready for merging. We will use only the PPT3 data for merging into the GPF data set. Also, let's change `round` and `group_code` to numeric for easier joining.

```{r}
library(dplyr)
ppt <- ppt %>%
    filter(data_type == "ppt3") %>%
    select(round, team_name, group_name, group_code, village, 
           union, union_code, upazila, upazila_code, 
           district, district_code, ward_number, producer_type,
           female_producers_involved, male_producers_involved,
           female_producers_present, male_producers_present,
           female_producers_dropout, male_producers_dropout,
           evaluation_date, facilitator,
           development_plan, rules_regulation, leadership_process,
           learning_sharing_space, services,
           cow_shed_mgmt, feed_mgmt, health_mgmt, breed_dvmt,
           milk_mgmt, milk_marketing, info_mgmt, gender_equity, total) %>%
    mutate(round = as.numeric(round),
           group_code = as.numeric(group_code))
dim(ppt)
mean(is.na(ppt$group_code))
```

Now let's prepare the GPF data for merging. For rounds 2, 3, and 4, group codes are missing so we need to construct them from the producer code/ID. (Also, we'll do this for round 5 because the group codes are not consistently correct in round 5.)

```{r}
library(stringr)

# gpf %>% 
#      select(group_code, producer_id) %>% 
#      mutate(group_code_new = str_sub(producer_id, end = 6)) %>% 
#      View()
# 
# gpf %>% 
#     select(group_code, producer_id) %>% 
#     mutate(group_code_new = if_else(is.na(group_code),
#                                     ifelse(nchar(str_sub(producer_id, end = 6)) == 6, 
#                                             str_sub(producer_id, end = 6),
#                                             NA),
#                                     group_code)) %>%
#     mutate(group_code_new = ifelse(nchar(group_code_new) == 6, group_code_new, NA)) %>%
#     View()

gpf <- gpf %>% 
    mutate(round = as.numeric(round)) %>%
    mutate(group_code = if_else(round != 1,
                                ifelse(nchar(str_sub(producer_id, end = 11)) == 11,
                                       str_sub(producer_id, end = 11),
                                       NA), 
                                group_code))
```

Now let's deal with round 1. The group codes and producer codes/IDs changed between round 1 and round 2. Let's use a separate document that will hopefully connect these two sets of codes.

```{r}
library(readxl)
producer_profile <- read_excel("../data/Final Producer Profile _SDVC-II_ 05.07.2014.xlsx",
                               sheet = 1, col_types = rep("text", 56))
producer_profile <- producer_profile %>%
    mutate(group_code_old = `Old LG Code`,
           group_code_new = `Group Code`,
           producer_id = `Producer's Code`,
           producer_serial = `Producer's serial # at group`)

transform_group_codes <- producer_profile %>% 
    select(group_code_old,
           group_code_new) %>%
    group_by(group_code_old) %>% 
    distinct(group_code_old, .keep_all = TRUE) %>% 
    filter(!is.na(group_code_old))

transform_group_codes
```

Now let's join and substitute these values into the GPF data.

```{r}
gpf <- gpf %>% 
    left_join(transform_group_codes, by = c("group_code" = "group_code_old")) %>%
    mutate(group_code = if_else(round == 1,
                                group_code_new, 
                                group_code)) %>%
    select(-group_code_new) %>%
    mutate(group_code = as.numeric(group_code))
```


That helped A LOT; now we just mostly have `NA` values in group code where we have control group producers who were not in a group.

```{r}
gpf %>% group_by(round) %>% summarize(mean_NA = mean(is.na(group_code)))
```

We expect the group codes in round 5 to be about 1/2 `NA` values because of the control producers. What is going on in round 1?

```{r}
gpf %>% filter(round == 1) %>% 
    group_by(household_type) %>% 
    summarize(mean_NA = mean(is.na(group_code)))
```

So the only group codes we recovered by doing the join with the new document were ~75% of the type 1 households. Hopefully that is OK?

Now let's deal with the producer IDs, which also changed between round 1 and round 2.

```{r}
transform_producer_ids <- producer_profile %>%
    select(group_code_old, producer_serial, producer_id) %>%
    mutate(producer_id_old = str_c(group_code_old, producer_serial),
           producer_id_new = producer_id) %>%
    select(producer_id_old, producer_id_new) %>%
    distinct(producer_id_old, .keep_all = TRUE) %>% 
    filter(!is.na(producer_id_old))

transform_producer_ids    
```

Now let's join and substitute these values into the GPF data.

```{r}
gpf <- gpf %>% 
    left_join(transform_producer_ids, by = c("producer_id" = "producer_id_old")) %>%
    mutate(producer_id = if_else(round == 1,
                                 producer_id_new, 
                                 producer_id)) %>%
    select(-producer_id_new)
```

That worked! How many producers in round 1 did not get matched up?

```{r}
gpf %>% filter(round == 1) %>% 
    group_by(household_type) %>% 
    summarize(matched = mean(is.na(nchar(producer_id))))
```

So about 65% of the type 1 producers from round 1 were matched to new producer IDs.

## Merging the Two Sets Together

Now we can merge them together using a join.

```{r}
gpf_ppt_merged <-  left_join(gpf, ppt, 
                             by = c("group_code", "round"),
                             suffix = c("_gpf", "_ppt"))
```

How big is this now?

```{r}
dim(gpf_ppt_merged)
```

Let's check some `NA` values for quantities measured from GPF and PPT, to see if the pattern/amount makes sense.

```{r}
gpf_ppt_merged %>% 
    group_by(round) %>% 
    summarize(cow_rearing_NA = mean(is.na(cow_rearing)),
              gender_equity_NA = mean(is.na(gender_equity)))
```

We expect about round 5 to have about 1/2 `NA` values for the PPT data because they have control producers in them; round 1 has about the same proportion of `NA` values as above.

## Writing the File

Let's save this as a csv.

```{r}
write_csv(gpf_ppt_merged, "../data/gpf_ppt_merged.csv")
```

