---
title: "Merging the PPT + GPF + DFT Datasets"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

It is now time to merge the DFT dataset with the already merged PPT and GPF datasets. Let's do it!

## Reading in All the Data

First, let's read in the merged version of the PPT + GPF data.

```{r}
library(readr)
gpf_ppt <- read_csv("../data/gpf_ppt_merged.csv", 
                    col_types = cols(.default = col_character()))
dim(gpf_ppt)
```

Now let's read in the DFT data.

```{r}
library(lubridate)
library(dplyr)
dft <- read_csv("../data/Correct and Reformatted DFT July 2014 to May 2016 Corrected CP Names+BRAC.csv",
                col_types = cols(.default = col_character()))
dim(dft)
dft <- dft %>%
    mutate(date = dmy(Date))
```

Let's change the `producer_id` and `round` to numeric in both data sets so we can join by them.

```{r}
gpf_ppt <- gpf_ppt %>%
    mutate(producer_id = as.numeric(producer_id_gpf),
           round = as.numeric(round))
dft <- dft %>%
    mutate(producer_id = as.numeric(Project.defined.Producer.s.Code))
```

How do we calculate round?

Many rows per producer -- what are we calculating?

## Merging the Two Sets Together

Now we can merge them together using a join.

```{r, eval = FALSE}
all_sdvc_merged <-  left_join(gpf_ppt, dft, 
                             by = c("producer_id", "round"))
```

How big is this now?

```{r, eval = FALSE}
dim(all_sdvc_merged)
```

## Writing the File

Let's save this as a csv.

```{r, eval = FALSE}
write_csv(all_sdvc_merged, "../data/all_sdvc_merged.csv")
```

