---
title: "Merging the PPT Datasets"
subtitle: "Strengthening the Dairy Value Chain"
author: "Julia Silge"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
---

```{r, echo = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, dpi = 180)
options(width=80, dplyr.width = 150)
```

There are five rounds of performance tracker data collected for this project, in September 2014 (May 2014), January 2015 (December 2014), December 2015 (June 2015), December 2015, and June 2016. These data sets contain the information we need to answer most of the questions for the final analysis plan, due this month, and is also expected to be the easiest to deal with, so let's work on munging, tidying, and merging the five data sets.

## Reading In the Data

First let's read in the original Excel files as sent to me zipped on 2016-9-8.

```{r}

library(readxl)
library(lubridate)

## to get the dates to read in as dates for this file, I find/replaced in Excel 
## in the date columns, all the - and . for / and a few other cleaning tasks
ppt1_round1 <- read_excel("../data/PPT-1&3 Database_1st round_May 2014_SDVC-II.xlsx", 
                          sheet = 1, col_types = rep("text", 58))
ppt1_round1$Date <- dmy(ppt1_round1$Date, tz = "Asia/Dhaka")
ppt3_round1 <- read_excel("../data/PPT-1&3 Database_1st round_May 2014_SDVC-II.xlsx", 
                          sheet = 2, col_types = rep("text", 30))
ppt3_round1$`Date of Evaluation` <- dmy(ppt3_round1$`Date of Evaluation`,
                                        tz = "Asia/Dhaka")

ppt1_round2 <- read_excel("../data/PPT-1&3 Database_2nd round_December 2014_SDVC-II.xls", 
                          sheet = 1, col_types = c(rep("text", 8), "date", rep("text", 37)))
ppt3_round2 <- read_excel("../data/PPT-1&3 Database_2nd round_December 2014_SDVC-II.xls", 
                          sheet = 2, col_types = c(rep("text", 13), "date", rep("text", 16)))

## I did end up having to remove some blank columns from the right hand side of this one 
## in Excel to get it to read it without NAs and without problems with colnames/colnums
ppt1_round3 <- read_excel("../data/PPT-1&3 Database_3rd Round_June 2015_SDVC-II.xlsx", 
                          sheet = 1, col_types = c(rep("text", 17), "date", rep("text", 39)))
ppt3_round3 <- read_excel("../data/PPT-1&3 Database_3rd Round_June 2015_SDVC-II.xls", 
                          sheet = 2, col_types = c(rep("text", 13), "date", rep("text", 16)))

ppt1_round4 <- read_excel("../data/PPT-1&3 Database_4th Round_ December 2015_SDVC-II.xls", 
                          sheet = 1, col_types = c(rep("text", 17), "date", rep("text", 40)))
ppt3_round4 <- read_excel("../data/PPT-1&3 Database_4th Round_ December 2015_SDVC-II.xls", 
                          sheet = 2, col_types = c(rep("text", 13), "date", rep("text", 16)))

## no date in this one
ppt1_round5 <- read_excel("../data/PPT-1&3 Database_5th Round_June 2016_SDVC-II.xlsx", 
                          sheet = 1, col_types = rep("text", 50))
ppt3_round5 <- read_excel("../data/PPT-1&3 Database_5th Round_June 2016_SDVC-II.xlsx", 
                          sheet = 2, col_types = c(rep("text", 14), "date", rep("text", 17)))
```


Let's save all of the column names as they are originally, for use later.

```{r}
library(dplyr)
original_names <- bind_rows(
    data_frame(ppt_type = 'ppt1', round = 1, names = list(names(ppt1_round1))),
    data_frame(ppt_type = 'ppt1', round = 2, names = list(names(ppt1_round2))),
    data_frame(ppt_type = 'ppt1', round = 3, names = list(names(ppt1_round3))),
    data_frame(ppt_type = 'ppt1', round = 4, names = list(names(ppt1_round4))),
    data_frame(ppt_type = 'ppt1', round = 5, names = list(names(ppt1_round5))),
    data_frame(ppt_type = 'ppt3', round = 1, names = list(names(ppt3_round1))),
    data_frame(ppt_type = 'ppt3', round = 2, names = list(names(ppt3_round2))),
    data_frame(ppt_type = 'ppt3', round = 3, names = list(names(ppt3_round3))),
    data_frame(ppt_type = 'ppt3', round = 4, names = list(names(ppt3_round4))),
    data_frame(ppt_type = 'ppt3', round = 5, names = list(names(ppt3_round5)))
    )
```

## Merging the PPT3 Data

The PPT3 Data all has about 30 columns; let's start by merging that. First, we need to make the names consistent.

```{r}
make_names_consistent <- function(df) {
    df %>% 
        rename(team_name = `Team Name`,
               group_name = `Group Name`,
               group_code = `Group Code`,
               village = `Village `,
               union = Union,
               upazila = Upazila,
               district = District,
               female_producers_involved = `Total # of Female Producers involve at the group`,
               male_producers_involved = `Total # of male Producers involve at the group`,
               female_producers_present = `# of Female Producers present at the session`,
               male_producers_present = `# of male Producers present at the session`,
               female_producers_dropout = `# of female  drop out`,
               male_producers_dropout = `# of male  drop out`,
               evaluation_date = `Date of Evaluation`,
               facilitator = `Name & designation of Facilitator:`,
               development_plan = `Group Operational & Dairy Development Plan\nGroup Operational & Dairy Development Plan\n`,
               rules_regulation = `Rules & Regulation\n`,
               leadership_process = `Leadership Process `,
               learning_sharing_space = `Learning Sharing Space`,
               services = `Access to Services/ External Relationship`,
               cow_shed_mgmt = `Project promoted Key practice adaptation status: Cow Shed Management`,
               feed_mgmt = `Project promoted Key practice adaptation status: Feed Management`,
               health_mgmt = `Project promoted Key practice adaptation status: Health Management`,
               breed_dvmt = `Project promoted Key practice adaptation status: Breed Development`,
               milk_mgmt = `Milk Management`,
               milk_marketing = `Milk Marketing`,
               info_mgmt = `Information Management (Record Keeping)`,
               gender_equity = `Gender Equity `,
               total = `Total `
        )
    }

ppt3_round1 <- ppt3_round1 %>%
    rename(producer_type = `Group Types (SDVC I&II=1; SDVC I&II=2)`) %>%
    make_names_consistent()

ppt3_round2 <- ppt3_round2 %>%
    rename(producer_type = `Group Status (SDVC I&II=1;\nSDVC II=2)`) %>%
    make_names_consistent()

ppt3_round3 <- ppt3_round3 %>%
    rename(producer_type = `Group Status (producers group from phase1=1 & Phase2 Group=2)`) %>%
    make_names_consistent()

ppt3_round4 <- ppt3_round4 %>%
    rename(producer_type = `Group Status (SDVC I&II=1; SDVC II=2)`) %>%
    make_names_consistent()

ppt3_round5 <- ppt3_round5 %>%
    rename(team_name = `1.1 Team name`,
           district = `1.2 District Name `,
           district_code = `District Code`,
           upazila = `1.3 Upazila`,
           upazila_code = `1.4 Upazila Code`,
           union = `1.5 Union Name`,
           union_code = `1.6 Union Code`,
           ward_number = `1.7 Ward Number`,
           village = `1.8 Village/Para Name`,
           group_name = `1.9 Group Name `,
           group_code = `Group Code`,
           producer_type = `Group Status (SDVC I&II=1; SDVC II=2)`,
           female_producers_present = `2.2 Number of female producers present at the session`,
           male_producers_present = `2.1 Number of male producers present at the session`,
           evaluation_date = `2.3 Date of evaluation`,
           facilitator_type = `2.4 Types of main facilitator`,
           facilitator = `2.5 Responsible FF`,
           development_plan = `3.1 Group Operational & Dairy Development Plan`,
           rules_regulation = `3.2 Rules & Regulations`,
           leadership_process = `3.3 Leadership Process `,
           learning_sharing_space = `3.4 Learning Sharing Space`,
           services = `3.5 Access to Services/ External Relationship`,
           cow_shed_mgmt = `3.6 Project promoted Key practice adaptation status: Cow Shed Management`,
           feed_mgmt = `3.7 Project promoted Key practice adaptation status: Feed Management`,
           health_mgmt = `3.8 Project promoted Key practice adaptation status: Health Management`,
           breed_dvmt = `3.9 Project promoted Key practice adaptation status: Breed Development`,
           milk_mgmt = `3.10 Milk Management`,
           milk_marketing = `3.11 Marketing `,
           info_mgmt = `3.12 Information Management (Record Keeping)`,
           gender_equity = `3.13 Gender Equity `,
           total = `Total Score `
        )

## remove column with NA column header that "corrupts" the data frame
ppt3_round5 <- ppt3_round5[,-32]

```

Now let's bind these rows together, and then use `select` to reorder the columns how we want them.

```{r}
ppt3 <- bind_rows(ppt3_round1 %>% mutate(round = 1), 
                  ppt3_round2 %>% mutate(round = 2), 
                  ppt3_round3 %>% mutate(round = 3), 
                  ppt3_round4 %>% mutate(round = 4), 
                  ppt3_round5 %>% mutate(round = 5)) %>%
    select(round, team_name, group_name, group_code, village, 
           union, union_code, upazila, upazila_code, 
           district, district_code, ward_number, producer_type,
           female_producers_involved, male_producers_involved,
           female_producers_present, male_producers_present,
           female_producers_dropout, male_producers_dropout,
           evaluation_date, facilitator,
           development_plan, rules_regulation, leadership_process,
           learning_sharing_space, services,
           cow_shed_mgmt, feed_mgmt, health_mgmt, breed_dvmt,
           milk_mgmt, milk_marketing, info_mgmt, gender_equity, total)
```

These are still all characters from when we first imported them from Excel, so let's convert the appropriate columns to numeric. This might make some `NA` values (the problem that led me to import everything as characters to start with) so let's make sure to check that.


```{r}
na_count_before <- sapply(ppt3, function(y) sum(length(which(is.na(y)))))

## now do the conversion
ppt3[,c(4,7,9,11:19,22:35)] <- lapply(ppt3[,c(4,7,9,11:19,22:35)], as.numeric)

na_count_after <-sapply(ppt3, function(y) sum(length(which(is.na(y)))))
na_count_after - na_count_before
```

Not bad; we just made 2 more `NA` values in this data frame of 3000 rows. I think this is OK. 

## Merging the PPT1 Data

Next, let's work on merging the PPT1 data. These files all have about 50 columns. Let's begin by making the names consistent. For starters, some of them have duplicate names for columns ("Men"/"Women"). Let's do these first.

```{r}
colnames(ppt1_round1)[c(8, 11, 14)] <- c("male_producers_involved",
                                         "male_producers_present",
                                         "male_producers_dropout")
colnames(ppt1_round1)[c(9, 12, 15)] <- c("female_producers_involved",
                                         "female_producers_present",
                                         "female_producers_dropout")

colnames(ppt1_round3)[c(9, 12, 15)] <- c("male_producers_involved",
                                          "male_producers_present",
                                          "male_producers_dropout")
colnames(ppt1_round3)[c(10, 13, 16)] <- c("female_producers_involved",
                                          "female_producers_present",
                                          "female_producers_dropout")

colnames(ppt1_round4)[c(9, 12, 15)] <- c("male_producers_involved",
                                          "male_producers_present",
                                          "male_producers_dropout")
colnames(ppt1_round4)[c(10, 13, 16)] <- c("female_producers_involved",
                                          "female_producers_present",
                                          "female_producers_dropout")
```


Now let's go through the bulk of the rest of the the column names.

```{r}
make_names_consistent <- function(df) {
    df %>% 
        rename(cowshed_cleanliness = `Clean cow shed and maintain disposal system regularly (cow dung & others)`,
               cowshed_light = `Proper ventilation , lights with sufficient security measurement available ( Window, sifficient light & air, net, smoke, finish liquid, coil  etc)`,
               hybrid_grass = `Produces Hybrid grass`,
               clean_grass = `Collected grass are ensured proper cleanliness during feeding`,
               feeds_bran_oil = `HH feeds at least any Bran and Oil cake`,
               ready_feed = `HH feeds their cattle any brand ready feed ( Ready Feed)`,
               feeds_vitamin = `HH feeds any type Vitamin mineral premix (DCP, DB mix, liquid)`,
               deworms = `HH regularly De-worm their all cattle except sick and pregnant cattle`,
               vaccinates = `HH  vaccinate their all cattle regularly except sick and pregnant cattle With given priority on Anthrax and FMD `,
               suggestion_from_vet = `Regular take suggestion / Treatment /check-up to the cattle health from the recommended Surgeon/paravate, LHW,etc `,
               ai_services = `HH taking  AI services for high breed/high milk production during this period`,
               milk_yesterday_volume = `Total milk volume (Yesterday) (in ltr.)`,
               increased_volume = `Increased volume of milk compare to before ( consider last 4 month)`,
               proper_milking = `HH knows the proper/recommended milking system (cleanliness of place, udder, teat and milking pot & complete milking practice)`,
               feed_after_milking = `Feeds the cow just after milking`,
               market_info = `Using market information for decision making`,
               selling_dft = `HH presently selling milk to DFT collection point`,
               satisfied_dft = `I am satisfied with overall DFT servise (payment, delivery, domentation etc)`,
               keeping_records = `Keeping record on individual milk production, sales and production cost `,
               group_saving = `I involve with group saving (weekly/monthly)`,
               borrowing_loan = `Taking loan from group saving/ others FI's easily for dairy purpose`,
               communicate_ku = `Frequintly communicate to input shops(KU) to purchase feed ,medicine and other services`,
               satisfied_ku = `I am satisfied with overall Krishi Utsho (KU) servises`,
               communicated_lhw = `Communicated with LHW and AI on treatment issues as when required`,
               satisfied_treatment = `I am satisfied with overall Treatment servises (dewarming, vaccination and AI)`,
               family_support = `My Spouse/other family members support me while I work to dairy purpose (Cow shed cleanning, fodder cultivation, feeding, milking etc)`,
               spent_income = `I spent comfortably the milk sales income for HH & own purpose as when required`,
               discuss_family = `I discussed with my family member regarding dairy related decision making`,
               decision_alone = `I can take decision along regarding dewarming, vaccination services as when required`,
               spoke_meeting = `I spoke comfortably in the group meeting `,
               consume_milk = `We consume our produced milk and gave preference to the children & women`
        )
    }

ppt1_round1 <- ppt1_round1 %>%
    rename(team_name = Team,
           group_name = `Group Name`,
           village = Village,
           union = ` Union  `,
           upazila = ` Upazilla  `,
           district = ` District `,
           producers_involved = `# of Producers involve in the group`,
           producers_present = `# of Producers present at the session`,
           producers_dropout = `# of drop out since last session`,
           facilitator = `Name & designation of Facilitator`,
           evaluation_date = Date,
           group_code_old = `Old Group ID`,
           group_code = `New Group ID`,
           producer_type = `Producer Type (SDVC I&II=1, SDVC II=2)`,
           producer_serial = Sl,
           producer_name = `Producer Name`,
           producer_id = `Producer ID`,
           sex = `Sex (Women=1/Man=2)`,
           guardian_name = `Spouse/Guardian Name `,
           group_leader = `Group Leader (Yes=1/No=0)`,
           total_cows = `# of total of cow`
           ) %>%
    make_names_consistent()


ppt1_round2 <- ppt1_round2 %>%
    rename(team_name = Team,
           group_name = `Group Name`,
           group_code = `Group Code`,
           village = Village,
           union = `Union  `,
           upazila = `Upazilla   `,
           district = `District `,
           facilitator = `Name & designation of Facilitator`,
           evaluation_date = `Date of Evaluation`,
           producer_name = `Producer Name`,
           producer_id = `Producer ID`,
           sex = `Sex (Women=1/Man=2)`,
           guardian_name = `Spouse/Guardian Name `,
           group_leader = `Group Leader (Yes=1/No=0)`,
           milk_yesterday_cows = `Yesterday's milk from how many cow?`
           ) %>%
    make_names_consistent()


ppt1_round3 <- ppt1_round3 %>%
    rename(team_name = `Team:`,
           group_name = `Group Name:`,
           group_code = `Group Code`,
           village = Village,
           union = ` Union:    `,
           upazila = ` Upazilla:   `,
           district = ` District: `,
           producers_involved = `# of Producers involve in the group:`,
           producers_present = `# of Producers present at the session:`,
           producers_dropout = `# of drop out since last session:`,
           facilitator = `Name & designation of Facilitator:`,
           evaluation_date = `Date:`,
           producer_serial = Sl,
           producer_name = `Producer Name`,
           producer_id = `Producer ID`,
           sex = `Sex (Women=1/Man=2)`,
           guardian_name = `Spouse/Guardian Name `,
           group_leader = `Group Leader (Yes=1/No=0)`,
           producer_type = `Producer Type (SDVC I&II=1; SDVC II=2)`,
           milk_yesterday_cows = `Yesterday milk how many cow?`) %>%
    make_names_consistent()


ppt1_round4 <- ppt1_round4 %>%
    rename(team_name = `Team:`,
           group_name = `Group Name:`,
           group_code = `Group Code`,
           village = Village,
           union = ` Union:    `,
           upazila = ` Upazilla:   `,
           district = ` District: `,
           producers_involved = `# of Producers involve in the group:`,
           producers_present = `# of Producers present at the session:`,
           producers_dropout = `# of drop out since last session:`,
           facilitator = `Name & designation of Facilitator:`,
           evaluation_date = Date,
           producer_serial = Sl,
           producer_name = `Producer Name`,
           producer_id = `Producer ID`,
           sex = `Sex (Women=1/Man=2)`,
           guardian_name = `Spouse/Guardian Name `,
           group_leader = `Group Leader (Yes=1/No=0)`,
           producer_type = `Producer Type (SDVC I&II=1; SDVC II=2)`,
           milk_yesterday_cows = `Yesterday milk how many cow?`) %>%
    make_names_consistent()

```


There are two columns for producer code in the following data frame. Are they all the same?

```{r}
data_frame(code1 = ppt1_round5$`Producer's Code`, code2 = ppt1_round5$`Producer Code`) %>% 
    mutate(compare = (code1 == code2)) 
data_frame(code1 = ppt1_round5$`Producer's Code`, code2 = ppt1_round5$`Producer Code`) %>% 
    mutate(compare = (code1 == code2)) %>% 
    summarize(compare_all = all(compare, na.rm = TRUE))

```

Yep, we can keep only one of them and throw the other one out.

```{r}
ppt1_round5 <- ppt1_round5 %>%
    rename(team_name = `Team Name`,
           district = District,
           upazila = Upazila,
           ward = `Union/Ward`,
           ward_number = `Ward #`,
           village = Village,
           para = Para,
           group_name = `Group Name`,
           group_code = `Group Code`,
           producer_id = `Producer Code`,
           producer_name = `Producer Name`,
           guardian_name = `Husbandand/ Father'S Name`,
           sex = `Sex (W=1, M=2)`,
           group_leader = `Group Leader  (Yes=1; No=0)`,
           producer_type = `Producer types (SDVC I&II=1; SDVC II=2)`,
           producer_serial = `Producer serial at group`,
           producer_status = `Producer Status`,
           cowshed_cleanliness = ` [1] Cowshed Cleanliness`,
           cowshed_light = ` [2] Sufficient Light and Ventilation in Cowshed`,
           hybrid_grass = ` [3] Produce Hybrid grass`,
           clean_grass = ` [4] Clean Collected Grass and Feed Cows`,
           feeds_bran_oil = ` [5] HH feeds at least any Bran and Oil cake`,
           feeds_vitamin = ` [6] HH feeds any type Vitamin mineral premix (DCP, DB mix, liquid)`,
           deworms = ` [7] HH regularly De-worm their all cattle except sick and pregnant cattle`,
           vaccinates = ` [9] HH  vaccinate their all cattle regularly except sick and pregnant cattle With given priority on Anthrax and FMD `,
           suggestion_from_vet = ` [10] Regular take suggestion / Treatment /check-up to the cattle health from the recommended Surgeon/paravate, LHW,etc `,
           ai_services = ` [11] HH taking  AI services for high breed/high milk production during this period`,
           milk_yesterday_cows = `[12] Yesterday's milk produced from how many cow?`,
           milk_yesterday_volume = `[13] Total milk volume yesterday (in ltr`,
           increased_volume = ` [14] Increased volume of milk compare to before ( consider last 4 month)`,
           proper_milking = ` [15] HH knows the proper/recommended milking system (cleanliness of place, udder, teat and milking pot & complete milking practice)`,
           feed_after_milking = ` [16] Feeds the cow just after milking`,
           market_info = ` [17] Using market information for decision making`,
           selling_dft = ` [18] HH presently selling milk to DFT collection point`,
           satisfied_dft = ` [19] I am satisfied with overall DFT servise (payment, delivery, domentation etc)`,
           keeping_records = ` [20] Keeping record on individual milk production, sales and production cost `,
           group_saving = ` [21] I involve with group saving (weekly/monthly)`,
           borrowing_loan = ` [22] Taking loan from group saving/ others FI's easily for dairy purpose`,
           communicate_ku = ` [23] Frequintly communicate to input shops(KU) to purchase feed ,medicine and other services`,
           satisfied_ku = ` [24] I am satisfied with overall Krishi Utsho (KU) servises`,
           communicated_lhw = ` [25] Communicated with LHW and AI on treatment issues as when required`,
           satisfied_treatment = ` [26] I am satisfied with overall Treatment servises (dewarming, vaccination and AI)`,
           family_support = ` [27] My Spouse/other family members support me while I work to dairy purpose (Cow shed cleanning, fodder cultivation, feeding, milking etc)`,
           spent_income = ` [28] I spent comfortably the milk sales income for HH & own purpose as when required`,
           discuss_family = ` [29] I discusse with my family member regarding dairy related decision making`,
           decision_alone = ` [30] I can take decision alone regarding dewarming, vaccination services as when required`,
           spoke_meeting = ` [31] I spoke comfortably in the group meeting `,
           consume_milk = ` [32] We consume our produced milk and gave preference to the children & women`
           )

```

Now let's bind these rows together, and then use `select` to reorder the columns how we want them.

```{r}
ppt1 <- bind_rows(ppt1_round1 %>% mutate(round = 1), 
                  ppt1_round2 %>% mutate(round = 2), 
                  ppt1_round3 %>% mutate(round = 3), 
                  ppt1_round4 %>% mutate(round = 4), 
                  ppt1_round5 %>% mutate(round = 5)) %>%
    select(round, team_name, group_name, group_code, group_code_old,
           village, para, union, upazila, district, ward, ward_number,
           producers_involved, female_producers_involved, male_producers_involved,
           producers_present, female_producers_present, male_producers_present,
           producers_dropout, female_producers_dropout, male_producers_dropout,
           evaluation_date, facilitator,
           producer_name, producer_id, producer_type, producer_serial, 
           producer_status, sex, guardian_name, group_leader,
           cowshed_cleanliness, cowshed_light, hybrid_grass, clean_grass,
           feeds_bran_oil, ready_feed, feeds_vitamin, deworms, vaccinates,
           suggestion_from_vet, ai_services, total_cows, milk_yesterday_cows,
           milk_yesterday_volume, increased_volume, proper_milking, feed_after_milking, 
           market_info, selling_dft, satisfied_dft, keeping_records, group_saving, 
           borrowing_loan, communicate_ku, satisfied_ku, communicated_lhw, 
           satisfied_treatment, family_support, spent_income, discuss_family,
           decision_alone, spoke_meeting, consume_milk)
```

These are still all characters from when we first imported them from Excel, so let's again convert the appropriate columns to numeric. Again, we will check whether this makes more `NA` values.

```{r}
na_count_before <- sapply(ppt1, function(y) sum(length(which(is.na(y)))))

## now do the conversion
ppt1[,c(4:5,12:21,25:27,29,31:63)] <- lapply(ppt1[,c(4:5,12:21,25:27,29,31:63)], as.numeric)

na_count_after <-sapply(ppt1, function(y) sum(length(which(is.na(y)))))
na_count_after - na_count_before
```

No new `NA` values! Perfect.

## Merging Both Together for Final PPT Data Set

Now we can merge the two types of PPT data together for the final version of the PPT data set.

```{r}
ppt <- bind_rows(ppt1 %>% mutate(data_type = 'ppt1'), 
                 ppt3 %>% mutate(data_type = 'ppt3')) %>%
    select(data_type, round, 
           team_name, group_name, group_code, group_code_old,
           village, para, union, union_code, upazila, upazila_code, 
           district, district_code, ward, ward_number,
           producers_involved, female_producers_involved, male_producers_involved,
           producers_present, female_producers_present, male_producers_present,
           producers_dropout, female_producers_dropout, male_producers_dropout,
           evaluation_date, facilitator,
           producer_name, producer_id, producer_type, producer_serial, 
           producer_status, sex, guardian_name, group_leader,
           cowshed_cleanliness, cowshed_light, hybrid_grass, clean_grass,
           feeds_bran_oil, ready_feed, feeds_vitamin, deworms, vaccinates,
           suggestion_from_vet, ai_services, total_cows, milk_yesterday_cows,
           milk_yesterday_volume, increased_volume, proper_milking, feed_after_milking, 
           market_info, selling_dft, satisfied_dft, keeping_records, group_saving, 
           borrowing_loan, communicate_ku, satisfied_ku, communicated_lhw, 
           satisfied_treatment, family_support, spent_income, discuss_family,
           decision_alone, spoke_meeting, consume_milk,
           development_plan, rules_regulation, leadership_process,
           learning_sharing_space, services,
           cow_shed_mgmt, feed_mgmt, health_mgmt, breed_dvmt,
           milk_mgmt, milk_marketing, info_mgmt, gender_equity, total)
```

We did it! What does this look like?

```{r}
dim(ppt)
kable(head(ppt, n = 20))
```

Let's save this as a csv.

```{r}
library(readr)
write_csv(ppt, "../data/ppt_merged.csv")
```

Let's also save the original names as a csv to be able to look at.

```{r}
library(tidyr)
write_csv(original_names %>% unnest(names), "../data/ppt_original_names.csv")
```

